Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-07-21 Paper/Poster/poster.tex
done maybe...

\vspace{-.3cm}
\makebox[\columnwidth]{ % replace framebox by makebox
\hspace{-4cm}
\begin{minipage}[l]{.78\columnwidth}
\myfig[0]{code_axis.ps}{.45}
\end{minipage}
\hspace{-3cm}
\begin{minipage}[l]{.4\columnwidth}
Typical learned codeword spanning $2$ bars, each bar
considered to be $4$ beats. Codebook size was $200$.
\end{minipage}
} % end framebox / makebox
\vspace{.5cm}

@@

Additional graphs on distortion, codeword size, etc, can be seen in the paper.
As expected, a larger codebook improves distortion, longer codewords are more
difficult to learn, and a larger training set improves the results.

\myfig[0]{codes1.ps}{.8}

\myfig[0]{close_patterns1.ps}{.8}

\myfig[0]{close_patterns_diff.ps}{.8}

@@

>>>>

\vspace{-.3cm}
\makebox[\columnwidth]{ % replace framebox by makebox
\hspace{-4cm}
\begin{minipage}[l]{.78\columnwidth}
\myfig[0]{code_axis.ps}{.45}
\end{minipage}
\hspace{-3.5cm}
\begin{minipage}[l]{.4\columnwidth}
Typical learned codeword spanning $2$ bars, each bar
considered to be $4$ beats. Codebook size was $200$.\\

A codewords can also be seen as the centroid of a cluster.
\end{minipage}
} % end framebox / makebox
\vspace{.5cm}

@@

\vspace{1.0cm}
Additional graphs on distortion, codeword size, etc, can be seen in the paper.
As expected, a larger codebook improves distortion, longer codewords are more
difficult to learn, and a larger training set improves the results.\\

Below are samples from actual codebooks and centroids.

\myfig[0]{codes1.ps}{.8}
% figure caption
\begin{center}
\begin{minipage}[c]{.7\columnwidth}
\begin{small}
The 25 codes most commonly used. 
Codes are from a $200$-entry codebook trained
on $2$ bars, $12 × 8$ patches. The proportion of patches accounted
for by each pattern is shown in parentheses.
\end{small}
\end{minipage}
\end{center}

\myfig[0]{close_patterns1.ps}{.8}
% figure caption
\begin{center}
\begin{minipage}[c]{.7\columnwidth}
\begin{small}
Cluster around first centroid (in \textit{introduction} section).
Random selection from a cluster of size $639$. 
This gives an intuition of the
variance in one cluster.
\end{small}
\end{minipage}
\end{center}

\myfig[0]{close_patterns_diff.ps}{.8}
% figure caption
\begin{center}
\begin{minipage}[c]{.7\columnwidth}
\begin{small}
First three patterns from figure above ($2$nd row) presented
with the centroid ($1$st row) and the absolute difference between 
both ($3$ row).
\end{small}
\end{minipage}
\end{center}

@@

% authors
\vspace{-2cm}
\myfig[0]{authors.eps}{.8}
% figure caption
\vspace{-2cm}
\begin{center}
\begin{minipage}[c]{.7\columnwidth}
\begin{center}
\begin{small}
Looking forward to discuss our work with you!
\end{small}
\end{center}
\end{minipage}
\end{center}
